B\'{e}zier $\bar{B}$ projection

### 2018-01-24 review_response.tex

\documentclass[10pt]{letter}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsbsy}
\usepackage{amscd}
\usepackage{times}
\usepackage{color}
\usepackage{ gensymb }

\newcommand{\qed}{\hfill \mbox{\raggedright \rule{.07in}{.1in}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% BEGIN: setup formating for works in progress.  Sets margins wider than normal,
% increases line spacing, and prints date of build on the title page and in the 
% footer of all other pages.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setlength\oddsidemargin{0.25in}
\setlength\evensidemargin{0.25in}
\setlength{\textwidth}{6.0in}
\setlength{\textheight}{8.0in}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% End formatting. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\signature{Michael J. Borden}
\begin{document}

\begin{letter}{Prof. T. J. R. Hughes, Editor \\ Computer Methods in Applied Mechanics and Engineering}

\opening{Dear Prof. Hughes,}

First of all, thank you for the editorial handling of our manuscript ``B\'{e}zier $\bar{B}$ Projection.''  We thank the reviewers for their thorough and detailed reviews of this manuscript.  We found the comments to be instructive and we have addressed them in the revised draft.  Our response to the comments from the reviewers are included below.  Based on the reviewers questions about convergence rates and the relationship between our formulation and mixed formulations we have added a number of sections that introduce a new formulation based on a mixed approach and investigate the convergence issues.  These section include: 5.2, 6.2, and 6.3.1 with additional discussion of the numerical results.  For clarity, we have included the reviewers comments, followed by our response, which we have highlighted in blue. Major changes in the submitted revised manuscript have been highlighted in blue.

\vspace{0.2in}
Best Regards,

Di Miao

\vspace{0.2in}
{\bf Reviewer \#1}: This manuscript extends the concept of B\'Åezier projection introduced in the paper CMAME 284:55-105, 2015 (cited reference [18]) to consider problems which exhibit internal constraints. The examples considered are the Timoshenko beam with increasing slenderness (L/t) and nearly incompressible linear elasticity. The manuscript is well written and subject to some minor changes should be accepted for publication in the Journal.

1) There are alternatives to the global L2 projection used for comparison in the paper. For example, see the papers: (a) The enhanced assumed strain method for the isogeometric analysis of nearly incompressible deformation of solids, by Cardoso and de Sa (JNME, 92:56-78, 2012) and (b) Isogeometric analysis of nearly incompressible solids, by Taylor (JNME, 87:273-288, 2011).

\begin{quote}
{\color{blue}
We thank the review for bringing these methods to our attention. We have made reference to them in the introduction of our paper, but do not include further comparisons because our methods are based on the L2 projection method.
}
\end{quote}

2) The example problems could include a more challenging test on performance for a near incompressible problem. A good example is the problem described in Sect 5.1 of A stabilized mixed finite element method for finite elasticity. Formulation for linear displacement and pressure interpolation, by O. Klaas et al. (CMAME, 180:65-79, 1999). The high confinement and strong stress gradients in this example provide for a much better test problem ‚Äì one which also does not have a singular point as exhibited in the Cook problem which probably has an effect in no unique asymptote in bottom of Figure 13.

\begin{quote}
{\color{blue}
We agree that this would be a good example for further study of the proposed method. However, the suggested example problem uses a Neo-Hookean model in a large deformation context, which would entail the extension of the proposed methods to the $\bar{F}$ formulation. In the authors opinion this requires a careful and comprehensive study and is left as the subject of a future work.
}
\end{quote}

3) The main difficulty with the proposed methodology is implementing in any existing finite element system based to element assembly as, for example, results for Kb in equation (49). Can this be overcome by using a mixed method, possibly with nodal parameters? This will certainly limit adoption of the proposed method in my view.

\begin{quote}
{\color{blue}
This is a very good question and has led to the addition of a non-symmetric formulation with a direct link to mixed formulations. In this additional formulation all matrices are formulated at the element level. We have kept the original symmetric formulation and believe it is still a useful approach. In the authors experience there are now many isogeometric codes that have moved beyond the need to strictly follow existing FEA element assembly routines so that adoption argument is not as strong as it once was.
}
\end{quote}

{\bf Reviewer \#2}: The paper presents a B-≠bar method based on BeÃÅzier projection coupled with IGA. IT presents some interesting new results that seem promising. I would like the authors to address the following comments.

In paragraphs 5.2 and 6.2, some of the notation used to define strain displacement matrices are not introduced. In addition, the structure of the dof storage is not presented, which would help understand the structure of the strain displacement arrays. I would recommend that some definition and a bit more details are given. This seems particularly important as the the first IGA B-≠bar paper (ref 38) does not present the method using strain displacement matrices.

\begin{quote}
{\color{blue}
We address this issue by adding the strain displacement matrices in equation (36), equation (37), equation (82) and equation (83).
}
\end{quote}

Plate with a hole example. As pointed out for p=3 and p=4 convergence rates are not optimal and for p=4, there is an increase in the error with the BeÃÅzier projection between the 2nd and 3rd meshes. The explanation regarding the conditioning of the stiffness matrix is very short. If this is indeed the case, i would expect to see table of conditioning number obtained with all cases to see the supposed degradation. Moreover the authors have not given any information regarding the linear algebra solver they are using. A more detailed study if this behaviour and its cause seems quite important.

\begin{quote}
    {\color{blue}
    We found the lose of rates is due to the inconsistency with the mixed formulation, we proposed a new non-symmetric formulation based on the mixed formulation which recovers the rates. 
    }
\end{quote}

In the examples for the linear incompressible elastic case, it would be interesting to show some plots for the stresses obtained with the method. As observed in the literature, for higher order functions, locking is sometimes not seen on displacement convergence plots. See for example the following reference : Isogeometric analysis of nearly incompressible large strain plasticity , T. Elguedj and T.J.R. Hughes, cmame 268, pp 388-416, 2014. Comparing stress contours for the standard, full B-bar and B\'ezier B-bar methods would be a plus to convince the reader of the efficiency and performance of the proposed method.

\begin{quote}
    {\color{blue}
    The stress convergence plots and stress error contour plots are added in figure 18 and figure 19.
    }
\end{quote}

The computational cost of the B\'ezier B-≠bar method is not discussed at all in the paper. I agree that obtaining a sparse matrix is an advantage over the classical B-bar method, but giving some information regarding the relative cost of forming the local stiffness matrices and assembly process would be interesting. Looking at paragraph 4.2, it seems that there are quite some operations to perform. Please give some comments and detailed information regarding the cost fo all 3 methods.

\begin{quote}
    {\color{blue}
    In the authors opinion comparing the cost of the methods is highly dependent on the implementation and has limited value. From a basic linear algebra accounting we know that the cost of solving dense systems is prohibitive for large problems. Perhaps this study could be the subject of a future work.
    }
\end{quote}

\end{letter}
\end{document}

### 2018-01-25 projection1120.tex
finished the change of stress plot

\begin{abstract}
  We demonstrate the use of B\'{e}zier projection to alleviate locking phenomena in structural mechanics applications of isogeometric analysis. \added{Based on two different 	
  interpretations of the well-known $\bar{B}$ projection, we propose two formulations and name them symmetric and non-symmetric B\'{e}zier $\bar{B}$ projection.} To demonstrate the utility of the \replaced{\Bezier projection}{approach} for both geometry and material locking phenomena we focus on transverse shear locking in Timoshenko beams and volumetric locking in nearly compressible linear elasticity although the approach can be applied generally to other types of locking phenemona as well. B\'{e}zier projection is a local projection technique with optimal approximation properties, which in many cases produces solutions that are comparable to global $L^2$ projection. In the context of $\bar{B}$ methods, the use of B\'ezier projection produces sparse stiffness matrices with only a slight increase in bandwidth when compared to standard displacement-based methods. Of particular importance is that the approach is applicable to any spline representation that can be written in B\'ezier form like NURBS, T-splines, LR-splines, etc. We discuss in detail how to integrate this approach into an existing finite element framework with minimal disruption through the use of B\'ezier extraction operators and a newly introduced dual \added{basis for} \Bezier \replaced{projection}{extraction} operator. We then demonstrate the behavior of the \replaced{two proposed formulations}{approach} through several challenging benchmark problems.
\end{abstract}
\keywords{Isogeometric analysis, B\'ezier extraction, \added{\Bezier dual basis}, B\'ezier projection, $\bar{B}$-projection, locking}
\section{Introduction}
Isogeometric analysis (IGA), introduced by Hughes et al. \cite{hughes_isogeometric_2005}, adopts the spline basis, which underlies the CAD geometry, as the basis for analysis. Of particular importance is the positive impact of smoothness on numerical solutions, where, in many application domains, IGA outperforms classical finite elements~\cite{cottrell_isogeometric_2009,cottrell_studies_2007,cottrell2006isogeometric,hughes_duality_2008,bazilevs_isogeometric_2010,evans_n-widths_2009}. Initial investigations of IGA focused on non-uniform rational B-splines (NURBS) due to their dominance in commercial CAD packages. However, many advances are being made in analysis-suitable geometry representations that overcome the strict rectangular topological restrictions of NURBS. Examples include T-splines~\cite{bazilevs_isogeometric_2010,sederberg_t-splines_2003} and their analysis-suitable restriction~\cite{scott_local_2012, li_analysis-suitable_2013}, hierarchical B-splines~\cite{bornemann_subdivision-based_2013,scott_isogeometric_2014,schillinger_isogeometric_2012,evans_hierarchical_2015,forsey_hierarchical_1988}, and locally refined B-splines~\cite{dokken_polynomial_2013,johannessen_isogeometric_2014} among others.

@@

Numerical locking in structural finite elements includes geometric locking in thin curved structural members such as membrane and shear locking and also includes volumetric locking in incompressible and nearly incompressible elasticity. There is an immense body of literature on approaches to overcome locking in the finite element community and various approaches have emerged as dominant. These include reduced quadrature~\cite{malkus_mixed_1978,zienkiewicz_reduced_1971}, $\bar{B}$ projection methods~\cite{nagtegaal_numerically_1974,hughes_generalization_1980}, and mixed methods based on the Hu-Washizu variational principle~\cite{dolbow_volumetric_1999,kasper_mixed-enhanced_2000,hughes_variational_1986}. It is important to mention that, although ameliorated at high polynomial degrees, smooth splines in the context of IGA still exhibit locking behavior~\cite{echter_numerical_2010, bouclier_locking_2012}.

@@

\sloppy Given the function spaces $\mathcal{S}(\Omega)=\{{\mathbf{u} \, \vert \, {\mathbf{u}\in{H^1(\Omega)\times{H^1(\Omega)}}},\mathbf{u}\vert_{\Gamma_{g}}=\mathbf{g}}\}$ and $\mathcal{V}(\Omega)=\{{\mathbf{w} \, \vert \, {\mathbf{w}\in{H^1(\Omega)\times{H^1(\Omega)}}}, \allowbreak \mathbf{w}\vert_{\Gamma_{g}}=\mathbf{0}}\}$ where $\mathbf{u}=\left\{{\omega,\phi}\right\}^T$, $\mathbf{w}=\left\{{\delta\omega,\delta\phi}\right\}^T$, $\mathbf{g}$ is the prescribed Dirichlet boundary condition, and $\Gamma_g$ is the Dirichlet boundary at $x=0$, the weak form of the problem can be stated as: find $\mathbf{u}\in{\mathcal{S}(\Omega)}$ such that for all $\mathbf{w}\in{\mathcal{V}(\Omega)}$
\begin{equation}
    {\int_{0}^L\kappa(\mathbf{w})EI\kappa(\mathbf{u}) + \bar{\gamma}(\mathbf{w})sGA\bar{\gamma}(\mathbf{u})} \, dx=\int_0^L\delta\omega f dx+\delta\omega(L)Q+\delta\phi(L)M.
\end{equation}
\deleted{and $\bar{\gamma}$ is the projected shear strain.}

\subsubsection{Discretization}
\replaced{We discretize $\omega$ and $\phi$ as}{We discretize $\mathbf{u}$ and $\mathbf{w}$ as}
\begin{align}
  \replaced{\omega = \sum_A \omega_A N_A}{\mathbf{u} = \sum_A \mathbf{U}_A N_A} \\
  \replaced{\phi = \sum_A \phi N_A}{\mathbf{u} = \sum_A \mathbf{U}_A N_A}
\end{align}
where \replaced{$N_A$ is a degree $p$ spline basis function, $\omega_A$ and $\phi_A$ are the corresponding control point values.}{$\mathbf{U}_A = \{\omega_A, \phi_A\}^T$ and $\mathbf{W}_A = \{\delta\omega_A, \delta\phi_A\}^T$ and $N_A$ is a degree $p$ spline basis function}. \added{The shear strain and bending strain can then be expressed as}
{\color{blue}\begin{align}
\gamma &= \sum_A{\begin{bmatrix}N'_A & -N_A\end{bmatrix}\begin{bmatrix}\omega_A & \phi_A\end{bmatrix}^T} \\
\kappa &= \sum_A\begin{bmatrix}0 & N'_A\end{bmatrix}\begin{bmatrix}\omega_A & \phi_A\end{bmatrix}^T
\end{align}}
The shear strain $\bar{\gamma}$ is constructed by B\'{e}zier projection of the true shear strain $\gamma$ onto a lower degree space. In other words, we project from a $p^{th}$ degree spline space with $n$ basis functions $\mathbf{N}$ defined by the knot vector
\begin{align}
\mathbf{\Xi}_{p}=\lbrace{\underbrace{0,0,\ldots,0}_\text{$p+1$ copies}},\mathbf{\Xi}_{int},{\underbrace{1,1,\ldots,1}_\text{$p+1$ copies}}\rbrace,
\label{eq:origin_knot_vector}
\end{align}
onto a $p-1^{th}$ degree spline space with $\bar{n}$ basis functions $\bar{\mathbf{N}}$ defined by the knot vector
\begin{equation}
\bar{\mathbf{\Xi}}_{p-1}=\lbrace{\underbrace{0,0,\ldots,0}_\text{$p$ copies}},\mathbf{\Xi}_{int},{\underbrace{1,1,\ldots,1}_\text{$p$ copies}}\rbrace
\label{eq:projected_knot_vector}
\end{equation}
where the internal knots, denoted by $\mathbf{\Xi}_{int}$, are the same for both spaces. The projected shear strain $\bar{\gamma}$ can then be written as
\begin{align}
  \bar{\gamma} &= \sum_A \bar{\gamma}_A \bar{N}_A.
\end{align}
The control variables $\bar{\gamma}_A$ are simply
\begin{align}
  \bar{\gamma}_A = \int_{\Omega^A} \hat{\bar{N}}_A \gamma \, d\Omega = \langle \hat{\bar{N}}_A, \gamma \rangle_{\Omega^i}
\end{align}
where $\hat{\bar{N}}_A$ is a dual basis function for the spline space of degree $p-1$ computed from \eqref{eq:local-dual-basis}.

Localizing to the B\'{e}zier element we define the strain-displacement arrays in terms of element Bernstein basis functions of degree $p$ and $p-1$ as
\begin{align}
	\mathbf{B}_e^\kappa 
    	&= \begin{bmatrix} 0 & -{B^e_{0,p}}' & \cdots & 0 & -{B^e_{p,p}}' \end{bmatrix}, \\
    \mathbf{B}_e^\gamma
    	&= \begin{bmatrix} {B^e_{0,p}}' & -B^e_{0,p} & \cdots & {B^e_{p,p}}' & -B^e_{p,p} \end{bmatrix}, \\
    \bar{\mathbf{B}}_e
    	&= \begin{bmatrix} \bar{B}^e_{0,p-1} & \cdots & \bar{B}^e_{p-1,p-1} \end{bmatrix},
\end{align}
\added{where $B^e_{i,p}$ is the $i^{th}$ Bernstein basis function of order $p$}. We can then compute the element arrays as
\begin{align}
\mathbf{K}_e^b &= EI\mathbf{C}^e\langle{{\mathbf{B}_e^\kappa}^T,\mathbf{B}_e^\kappa}\rangle(\mathbf{C}^e)^T, \label{eq:symmetric_timoshenko}\\
\bar{\mathbf{M}}_e &= s{GA}\bar{\mathbf{C}}^e\langle{\bar{\mathbf{B}}_e^T,\bar{\mathbf{B}}_e}\rangle(\bar{\mathbf{C}}^e)^T, \\
\replaced{\hat{\mathbf{P}}_e}{\mathbf{P}_e} &= \langle{(\hat{\bar{\mathbf{N}}}^e)^T,\mathbf{B}^\gamma_e}\rangle(\mathbf{C}^e)^T,
\end{align}
where $\mathbf{C}^e$ is the element extraction operator for the degree $p$ spline space, $\bar{\mathbf{C}}^e$ is the element extraction operator for the degree $p-1$ spline space, and $\hat{\bar{\mathbf{N}}}^e$ are the dual basis functions restricted to the element for the degree $p-1$ spline space. The global stiffness matrix can then be written as
\begin{align}
	\mathbf{K} = \mathbf{K}^b + \bar{\mathbf{K}}^s_S \label{eqn:symmetric_b_bar_timoshenko_stiffness}
\end{align}
where
\begin{align}
	\mathbf{K}^b &=\A_e\mathbf{K}_e^b,\label{eqn:bending_stiffness} \\
	\bar{\mathbf{K}}^s&=\replaced{\hat{\mathbf{P}}}{\mathbf{P}}^T\bar{\mathbf{M}}\replaced{\hat{\mathbf{P}}}{\mathbf{P}}\label{eqn:shear_stiffness} \\
	\replaced{\hat{\mathbf{P}}}{\mathbf{P}} &=\A_e\replaced{\hat{\mathbf{P}}_e}{\mathbf{P}_e} \\
    \bar{\mathbf{M}} &=\A_e\bar{\mathbf{M}}_e
\end{align}
and $\A$ is the standard finite element assembly operator \cite{hughes_finite_2012}. We note that the assembly of $\bar{\mathbf{K}}^s$ requires the assembly of two intermediate matrices, $\bar{\mathbf{M}}$ and $\replaced{\hat{\mathbf{P}}}{\mathbf{P}}$. The computation of these matrices is needed because the product of two integrals over the entire domain can not be localized to the element level.
\subsection{Non-symmetric \Bezier $\bar{B}$ projection}
\label{sec:non-symmetric}

@@

Convergence plots for the relative error of the displacement and energy in the $L^2$ norm are shown in Figure \ref{fig:platewithhole_convergence}. As can be seen, the standard $Q_p$ approximations suffer from severe volumetric locking for all orders while, on the other hand, the $\bar{B}$ methods remedy locking for all cases. \replaced{For the symmetric \Bezier $\bar{B}$ method, the optimality in all three measures has been obtained for biquadratic elements; the optimal energy convergence rate has been achieved for bicubic elements; however, the degradation of convergence rates in all three measures has been observed for biquartic elements. The can be attributed to the fact that the derivation of the symmetric \Bezier $\bar{B}$ method is purely based on the engineering analogy between the $L^2$ projection and \Bezier projection. On the other hand, the non-symmetric \Bezier $\bar{B}$ method, derived from the mixed formulation, is optimal for displacement, stress and energy for all elements with slightly higher errors than that of global $\bar{B}$ method, which agrees with the inf-sup test.}{For biquadratic elements, the \Bezier $\bar{B}$ method obtains optimal convergence rates for both the displacement and energy error, and the difference in the energy error between the global $\bar{B}$ and the B\'ezier $\bar{B}$ methods is indistinguishable. For bicubic and biquartic elements, the convergence rates of the B\'ezier $\bar{B}$ method for the energy error are optimal. The convergence rates of B\'ezier $\bar{B}$ method for the displacement error, however, are not optimal. This degradation in the rates can likely be attributed to the conditioning of the Bernstein basis and the element extraction operators.}\par

\added{Contour plots of the error in $\sigma_{xx}$ for biquartic elements of the most refined mesh are shown in Figure \ref{fig:platewithhole_contour}, We can see from these plots that $Q_4$ elements have severe error while the projection methods all reduce error to a more acceptable level. Here we can also see that the non-symmetric method has a slight improvement compared to the symmetric method.}
\begin{figure}[h]
    \center
\begin{tabular}{ccc}
\includegraphics[width=.31\linewidth]{deformation_p_2} & \includegraphics[width=.31\linewidth]{deformation_p_3} & \includegraphics[width=.31\linewidth]{deformation_p_4}\\
\includegraphics[width=.31\linewidth]{stress_p_2} & \includegraphics[width=.31\linewidth]{stress_p_3} & \includegraphics[width=.31\linewidth]{stress_p_4}\\
\includegraphics[width=.31\linewidth]{energy_p_2} & \includegraphics[width=.31\linewidth]{energy_p_3} & \includegraphics[width=.31\linewidth]{energy_p_4}
\end{tabular}
    \caption{Convergence study of the plate with a circular hole. The relative $L^2$ error of displacement, stress and the relative error in energy norm with respect to mesh refinement.}
	\label{fig:platewithhole_convergence}
\end{figure}

>>>>

\begin{abstract}
  We demonstrate the use of B\'{e}zier projection to alleviate locking phenomena in structural mechanics applications of isogeometric analysis. \added{Based on two different 	
  interpretations of the well-known $\bar{B}$ projection, we propose two formulations and name them symmetric and non-symmetric B\'{e}zier $\bar{B}$ projection.} To demonstrate the utility of the \added{\Bezier projection} for both geometry and material locking phenomena we focus on transverse shear locking in Timoshenko beams and volumetric locking in nearly compressible linear elasticity although the approach can be applied generally to other types of locking phenemona as well. B\'{e}zier projection is a local projection technique with optimal approximation properties, which in many cases produces solutions that are comparable to global $L^2$ projection. In the context of $\bar{B}$ methods, the use of B\'ezier projection produces sparse stiffness matrices with only a slight increase in bandwidth when compared to standard displacement-based methods. Of particular importance is that the approach is applicable to any spline representation that can be written in B\'ezier form like NURBS, T-splines, LR-splines, etc. We discuss in detail how to integrate this approach into an existing finite element framework with minimal disruption through the use of B\'ezier extraction operators and a newly introduced dual \added{basis for} \Bezier \added{projection} operator. We then demonstrate the behavior of the two proposed formulations through several challenging benchmark problems.
\end{abstract}
\keywords{Isogeometric analysis, B\'ezier extraction, \added{\Bezier dual basis}, B\'ezier projection, $\bar{B}$-projection, locking}
\section{Introduction}
Isogeometric analysis (IGA), introduced by Hughes et al. \cite{hughes_isogeometric_2005}, adopts the spline basis, which underlies the CAD geometry, as the basis for analysis. Of particular importance is the positive impact of smoothness on numerical solutions, where, in many application domains, IGA outperforms classical finite elements~\cite{cottrell_isogeometric_2009,cottrell_studies_2007,cottrell2006isogeometric,hughes_duality_2008,bazilevs_isogeometric_2010,evans_n-widths_2009}. Initial investigations of IGA focused on non-uniform rational B-splines (NURBS) due to their dominance in commercial CAD packages. However, many advances are being made in analysis-suitable geometry representations that overcome the strict rectangular topological restrictions of NURBS. Examples include T-splines~\cite{bazilevs_isogeometric_2010,sederberg_t-splines_2003} and their analysis-suitable restriction~\cite{scott_local_2012, li_analysis-suitable_2013}, hierarchical B-splines~\cite{bornemann_subdivision-based_2013,scott_isogeometric_2014,schillinger_isogeometric_2012,evans_hierarchical_2015,forsey_hierarchical_1988}, and locally refined B-splines~\cite{dokken_polynomial_2013,johannessen_isogeometric_2014} among others.

@@

Numerical locking in structural finite elements includes geometric locking in thin curved structural members such as membrane and shear locking and also includes volumetric locking in incompressible and nearly incompressible elasticity. There is an immense body of literature on approaches to overcome locking in the finite element community and various approaches have emerged as dominant. These include reduced quadrature~\cite{malkus_mixed_1978,zienkiewicz_reduced_1971}, $\bar{B}$ projection methods~\cite{nagtegaal_numerically_1974,hughes_generalization_1980, NME:NME4328}, and mixed methods based on the Hu-Washizu variational principle~\cite{dolbow_volumetric_1999,kasper_mixed-enhanced_2000,hughes_variational_1986, NME:NME3048}. It is important to mention that, although ameliorated at high polynomial degrees, smooth splines in the context of IGA still exhibit locking behavior~\cite{echter_numerical_2010, bouclier_locking_2012}.

@@

\sloppy Given the function spaces $\mathcal{S}(\Omega)=\{{\mathbf{u} \, \vert \, {\mathbf{u}\in{H^1(\Omega)\times{H^1(\Omega)}}},\mathbf{u}\vert_{\Gamma_{g}}=\mathbf{g}}\}$ and $\mathcal{V}(\Omega)=\{{\mathbf{w} \, \vert \, {\mathbf{w}\in{H^1(\Omega)\times{H^1(\Omega)}}}, \allowbreak \mathbf{w}\vert_{\Gamma_{g}}=\mathbf{0}}\}$ where $\mathbf{u}=\left\{{\omega,\phi}\right\}^T$, $\mathbf{w}=\left\{{\delta\omega,\delta\phi}\right\}^T$, $\mathbf{g}$ is the prescribed Dirichlet boundary condition, and $\Gamma_g$ is the Dirichlet boundary at $x=0$, the weak form of the problem can be stated as: find $\mathbf{u}\in{\mathcal{S}(\Omega)}$ such that for all $\mathbf{w}\in{\mathcal{V}(\Omega)}$
\begin{equation}
    {\int_{0}^L\kappa(\mathbf{w})EI\kappa(\mathbf{u}) + \bar{\gamma}(\mathbf{w})sGA\bar{\gamma}(\mathbf{u})} \, dx=\int_0^L\delta\omega f dx+\delta\omega(L)Q+\delta\phi(L)M.
\end{equation}

\subsubsection{Discretization}
\added{We discretize $\omega$ and $\phi$ as}
\begin{align}
  \added{\omega = \sum_A \omega_A N_A} \\
  \added{\phi = \sum_A \phi N_A}
\end{align}
where \added{$N_A$ is a degree $p$ spline basis function, $\omega_A$ and $\phi_A$ are the corresponding control point values.}. \added{The shear strain and bending strain can then be expressed as}
{\color{blue}\begin{align}
\gamma &= \sum_A{\begin{bmatrix}N'_A & -N_A\end{bmatrix}\begin{bmatrix}\omega_A & \phi_A\end{bmatrix}^T} \\
\kappa &= \sum_A\begin{bmatrix}0 & N'_A\end{bmatrix}\begin{bmatrix}\omega_A & \phi_A\end{bmatrix}^T
\end{align}}
The shear strain $\bar{\gamma}$ is constructed by B\'{e}zier projection of the true shear strain $\gamma$ onto a lower degree space. In other words, we project from a $p^{th}$ degree spline space with $n$ basis functions $\mathbf{N}$ defined by the knot vector
\begin{align}
\mathbf{\Xi}_{p}=\lbrace{\underbrace{0,0,\ldots,0}_\text{$p+1$ copies}},\mathbf{\Xi}_{int},{\underbrace{1,1,\ldots,1}_\text{$p+1$ copies}}\rbrace,
\label{eq:origin_knot_vector}
\end{align}
onto a $p-1^{th}$ degree spline space with $\bar{n}$ basis functions $\bar{\mathbf{N}}$ defined by the knot vector
\begin{equation}
\bar{\mathbf{\Xi}}_{p-1}=\lbrace{\underbrace{0,0,\ldots,0}_\text{$p$ copies}},\mathbf{\Xi}_{int},{\underbrace{1,1,\ldots,1}_\text{$p$ copies}}\rbrace
\label{eq:projected_knot_vector}
\end{equation}
where the internal knots, denoted by $\mathbf{\Xi}_{int}$, are the same for both spaces. The projected shear strain $\bar{\gamma}$ can then be written as
\begin{align}
  \bar{\gamma} &= \sum_A \bar{\gamma}_A \bar{N}_A.
\end{align}
The control variables $\bar{\gamma}_A$ are simply
\begin{align}
  \bar{\gamma}_A = \int_{\Omega^A} \hat{\bar{N}}_A \gamma \, d\Omega = \langle \hat{\bar{N}}_A, \gamma \rangle_{\Omega^i}
\end{align}
where $\hat{\bar{N}}_A$ is a dual basis function for the spline space of degree $p-1$ computed from \eqref{eq:local-dual-basis}.

Localizing to the B\'{e}zier element we define the strain-displacement arrays in terms of element Bernstein basis functions of degree $p$ and $p-1$ as
\begin{align}
	\mathbf{B}_e^\kappa 
    	&= \begin{bmatrix} 0 & -{B^e_{0,p}}' & \cdots & 0 & -{B^e_{p,p}}' \end{bmatrix}, \\
    \mathbf{B}_e^\gamma
    	&= \begin{bmatrix} {B^e_{0,p}}' & -B^e_{0,p} & \cdots & {B^e_{p,p}}' & -B^e_{p,p} \end{bmatrix}, \\
    \bar{\mathbf{B}}_e
    	&= \begin{bmatrix} \bar{B}^e_{0,p-1} & \cdots & \bar{B}^e_{p-1,p-1} \end{bmatrix},
\end{align}
\added{where $B^e_{i,p}$ is the $i^{th}$ Bernstein basis function of order $p$}. We can then compute the element arrays as
\begin{align}
\mathbf{K}_e^b &= EI\mathbf{C}^e\langle{{\mathbf{B}_e^\kappa}^T,\mathbf{B}_e^\kappa}\rangle(\mathbf{C}^e)^T, \label{eq:symmetric_timoshenko}\\
\bar{\mathbf{M}}_e &= s{GA}\bar{\mathbf{C}}^e\langle{\bar{\mathbf{B}}_e^T,\bar{\mathbf{B}}_e}\rangle(\bar{\mathbf{C}}^e)^T, \\
{\hat{\mathbf{P}}_e} &= \langle{(\hat{\bar{\mathbf{N}}}^e)^T,\mathbf{B}^\gamma_e}\rangle(\mathbf{C}^e)^T,
\end{align}
where $\mathbf{C}^e$ is the element extraction operator for the degree $p$ spline space, $\bar{\mathbf{C}}^e$ is the element extraction operator for the degree $p-1$ spline space, and $\hat{\bar{\mathbf{N}}}^e$ are the dual basis functions restricted to the element for the degree $p-1$ spline space. The global stiffness matrix can then be written as
\begin{align}
	\mathbf{K} = \mathbf{K}^b + \bar{\mathbf{K}}^s_S \label{eqn:symmetric_b_bar_timoshenko_stiffness}
\end{align}
where
\begin{align}
	\mathbf{K}^b &=\A_e\mathbf{K}_e^b,\label{eqn:bending_stiffness} \\
	\bar{\mathbf{K}}^s&={\hat{\mathbf{P}}}^T\bar{\mathbf{M}}{\hat{\mathbf{P}}}\label{eqn:shear_stiffness} \\
	{\hat{\mathbf{P}}} &=\A_e{\hat{\mathbf{P}}_e} \\
    \bar{\mathbf{M}} &=\A_e\bar{\mathbf{M}}_e
\end{align}
and $\A$ is the standard finite element assembly operator \cite{hughes_finite_2012}. We note that the assembly of $\bar{\mathbf{K}}^s$ requires the assembly of two intermediate matrices, $\bar{\mathbf{M}}$ and ${\hat{\mathbf{P}}}$. The computation of these matrices is needed because the product of two integrals over the entire domain can not be localized to the element level.
\subsection{Non-symmetric \Bezier $\bar{B}$ projection}
\label{sec:non-symmetric}

@@

Convergence plots for the relative error of the displacement and energy in the $L^2$ norm are shown in Figure \ref{fig:platewithhole_convergence}. As can be seen, the standard $Q_p$ approximations suffer from severe volumetric locking for all orders while, on the other hand, the $\bar{B}$ methods remedy locking for all cases. \added{For the symmetric \Bezier $\bar{B}$ method, the optimality in all three measures has been obtained for biquadratic elements; the optimal energy convergence rate has been achieved for bicubic elements; however, the degradation of convergence rates in all three measures has been observed for biquartic elements. The can be attributed to the fact that the derivation of the symmetric \Bezier $\bar{B}$ method is purely based on the engineering analogy between the $L^2$ projection and \Bezier projection. On the other hand, the non-symmetric \Bezier $\bar{B}$ method, derived from the mixed formulation, is optimal for displacement, stress and energy for all elements with slightly higher errors than that of global $\bar{B}$ method, which agrees with the inf-sup test.}\par

\added{Contour plots of  $\sigma_{xx}$ for biquartic elements of the finest mesh are shown in Figure \ref{fig:platewithhole_contour}. We denote that, for the finest mesh, results from all $\bar{B}$ methods are consistent with the refernce solution, while using standard finite element still leads to a huge error. Figure \ref{fig:platewithhole_error_contour} shows the absolute error of $\sigma_{xx}$ with the same mesh. As can be seen, the projection methods reduce error to an acceptable level (less than $.1\%$ of the maximal $\sigma_{xx}$) while the error the $Q_4$ element is at the same level of the maximal $\sigma_{xx}$. Here we can also see that the non-symmetric method has a slight improvement compared to the symmetric method.}
\begin{figure}[h]
    \center
\begin{tabular}{ccc}
\includegraphics[width=.31\linewidth]{deformation_p_2} & \includegraphics[width=.31\linewidth]{deformation_p_3} & \includegraphics[width=.31\linewidth]{deformation_p_4}\\
\includegraphics[width=.31\linewidth]{stress_p_2} & \includegraphics[width=.31\linewidth]{stress_p_3} & \includegraphics[width=.31\linewidth]{stress_p_4}\\
\includegraphics[width=.31\linewidth]{energy_p_2} & \includegraphics[width=.31\linewidth]{energy_p_3} & \includegraphics[width=.31\linewidth]{energy_p_4}
\end{tabular}
    \caption{Convergence study of the plate with a circular hole. The relative $L^2$ error of displacement, stress and the relative error in energy norm with respect to mesh refinement.}
	\label{fig:platewithhole_convergence}
\end{figure}

\begin{figure}[htb!]
    \center
    \begin{tabular}{cc}
    \includegraphics[width=.4\linewidth]{no_stress_contour} & \includegraphics[width=.4\linewidth]{g_stress_contour}\\
    $Q_4$ & $\mathcal{T}^{L^2} Q_4/Q_3$\\
    \includegraphics[width=.4\linewidth]{s_stress_contour} & \includegraphics[width=.4\linewidth]{ns_stress_contour}\\
    $S-\mathcal{T}^{p} Q_4/Q_3$ & $NS-\mathcal{T}^{p} Q_4/Q_3$\\
    \includegraphics[width=.4\linewidth]{reference_stress_contour} & \includegraphics[width=.14\linewidth]{legend}\\
    Reference & Legend
    \end{tabular}
        \caption{ Contour plots of $\sigma_{xx}^h$ for the plate with a circular hole ($p=4$, and the finest mesh is used).}
        \label{fig:platewithhole_contour}
\end{figure}
